---
title: "Bechdel Test"
author: "Created by Mine Çetinkaya-Rundel"
output: github_document
---
<!--- you might change html_document to github_document if you are working with GitHub--->

```{r setup, include = FALSE}
knitr::opts_chunk$set(comment = "")
```


In this mini analysis we work with the data used in the FiveThirtyEight story titled ["The Dollar-And-Cents Case Against Hollywood's Exclusion of Women"](https://fivethirtyeight.com/features/the-dollar-and-cents-case-against-hollywoods-exclusion-of-women/).

1. Your task is to fill in the blanks denoted by `___` with text or code.  
2. Fix any errors.  
3. Identify specific R code function and how you looked them up.  

## Data and packages

We start with loading the packages we'll use.

```{r load-packages, message=FALSE}
library(fivethirtyeight)
library(tidyverse)
```

The dataset contains information on `r nrow(bechdel)` movies released between `r min(bechdel$year)` and `r max(bechdel$year)`.
However we'll focus our analysis on movies released between 1990 and 2013.

```{r}
bechdel90_13 <- bechdel %>% filter(between(year, 1990, 2013))
```

> What is the `%>%` inside the code? What does it do? How did you determine your answer?   

__%>% is a Pipe Operator. It allows the variable being referenced to be passed into another function. I this case, the result of the 'filter' function is being stored into bechdel90_13 after bechdel is assigned to bechdel90_13.__



There are `r nrow(bechdel90_13)` such movies.

The financial variables we'll focus on are the following:

-   `budget_2013`: Budget in 2013 inflation adjusted dollars
-   `domgross_2013`: Domestic gross (US) in 2013 inflation adjusted dollars
-   `intgross_2013`: Total International (i.e., worldwide) gross in 2013 inflation adjusted dollars

And we'll also use the `binary` and `clean_test` variables for **grouping**.

## Analysis

Let's take a look at how median budget and gross vary by whether the movie passed the Bechdel test, which is stored in the `binary` variable.

```{r message = FALSE}
bechdel90_13 %>%
  group_by(binary) %>%
  summarise(med_budget = median(budget_2013),
            med_domgross = median(domgross_2013, na.rm = TRUE),
            med_intgross = median(intgross_2013, na.rm = TRUE))
```

> What does `summarise()` do? How did you look it up?  
I looked up summarise() in the help section. What it does is it turns a group of variales into a data frame. This allows you to quickly group information that is similar to each other. 




Next, let's take a look at how median budget and gross vary by a more detailed indicator of the Bechdel test result.
This information is stored in the `clean_test` variable, which takes on the following values:

-   `ok` = passes test
-   `dubious`
-   `men` = women only talk about men
-   `notalk` = women don't talk to each other
-   `nowomen` = fewer than two women

```{r message = FALSE}
bechdel90_13 %>%
  group_by(clean_test) %>%  #fill in the gap with the right variable
  summarise(med_budget = median(budget_2013),
            med_domgross = median(domgross_2013, na.rm = TRUE),
            med_intgross = median(intgross_2013, na.rm = TRUE))
```

In order to evaluate how return on investment varies among movies that pass and fail the Bechdel test, we'll first create a new variable called `roi` as the ratio of the gross to budget.

```{r}
bechdel90_13 <- bechdel90_13 %>%
  mutate(roi = (intgross_2013 + domgross_2013) / budget_2013)
```


Let's see which movies have the highest return on investment.

```{r}
bechdel90_13 %>%
  arrange(desc(roi)) %>% 
  select(title, roi, year)
```

> What does `select()` do? How did you look it up?  
Select (according to the help section) is a Tidyverse function that returns a subset of a data frame.




Below is a visualization of the return on investment by test result, however it's difficult to see the distributions due to a few extreme observations.

```{r warning = FALSE}
ggplot(data = bechdel90_13, 
       mapping = aes(x = clean_test, y = roi, color = binary)) +
  geom_boxplot() +
  labs(title = "Return on investment vs. Bechdel test result",
       x = "Detailed Bechdel result",
       y = "Investment Return",
       color = "Binary Bechdel result")
```

What are those movies with *very* high returns on investment?

```{r}
bechdel90_13 %>%
  filter(roi > 400) %>%
  select(title, budget_2013, domgross_2013, year)
```

Zooming in on the movies with `roi < 200` provides a better view of how the medians across the categories compare:

```{r warning = FALSE}
ggplot(data = bechdel90_13, mapping = aes(x = clean_test, y = roi, color = binary)) +
  geom_boxplot() +
  labs(title = "Return on investment vs. Bechdel test result",
       subtitle = "Zooming in to movies with ROI < 15", # Something about zooming in to a certain level
       x = "Detailed Bechdel result",
       y = "Return on investment",
       color = "Binary Bechdel result") +
  coord_cartesian(ylim = c(0, 15))
```


> What did you learn from the data analysis included in the document?  
The most common error here are missing functions and variables. One has to be very careful of how they make variables otherwise they will not be found. The same goes for importing libraries.


